About {\bf llvm2aa}

### 2013-05-11 v2/llvmbc2Aa/docs/llvm2aa.tex
updated the pipe_dispatch example to use my_strcmp to do string matches..
Also, added comment line option in modules.txt
and updated llvm2aa documentation
updated documentation to reflect changes.
Committing changes to llvm2aa for suppression of do-while extraction when a special function is called in the loop.

The options:
\begin{itemize}
\item {\bf --modules=listfile} : Specify the list of functions in the bytecode
which should be converted to \Aa.   The names of these functions should be
listed in the text-file listfile. If this option is not specified, all functions
are converted.
\item {\bf --storageinit} :  Storage objects in the llvm bytecode
are explicitly initialized in the generated \Aa code.   An initializer
routine {\bf global\_storage\_initializer\_} is instantiated in
the \Aa code for this purpose.
\item {\bf -pipedepths=depthfile} : Specify the maximum depths of
pipes in the generated Aa program. The file ``depthfile'' is a list
of pairs (one pair per line).  The first element of the pair specifies
a pipe name, and the second, its maximum depth.   The default depth
of any pipe is $1$.
\item {\bf llvm2aa} uses the LLVM compiler
infrastructure to perform LLVM byte-code optimizations.  A large list
of these optimizations is available through the llvm2aa command-line.
For more details, see LLVM documentation at http://www.llvm.org.
\end{itemize}

>>>>

The options:
\begin{itemize}
\item {\bf --modules=listfile} : Specify the list of functions in the bytecode
which should be converted to \Aa.   The names of these functions should be
listed in the text-file listfile.  One function name must be present
on each line (the {\bf exact} function name should be provided on the line, without leading
or trailing spaces).  Lines which start with the character '\#' are
ignored as comments.  If this option is not specified, all functions
are converted.  
\item {\bf --storageinit} :  Storage objects in the llvm bytecode
are explicitly initialized in the generated \Aa code.   An initializer
routine {\bf global\_storage\_initializer\_} is instantiated in
the \Aa code for this purpose.
\item {\bf -pipedepths=depthfile} : Specify the maximum depths of
pipes in the generated Aa program. The file ``depthfile'' is a list
of pairs (one pair per line).  The first element of the pair specifies
a pipe name, and the second, its maximum depth.   The default depth
of any pipe is $1$.
\item {\bf -extract\_do\_while=true}: If specified, mark inner loops
as do-while loops, whose implementation will be
pipelined.  An inner loop is a basic block whose terminator
statement has a branch back to the beginning of the basic block. 
This optimization is suppressed if the inner loop body contains a
call to the special function {\bf nooptimize}.  If not specified,
inner loops are not marked as do-while loops.
\item {\bf llvm2aa} uses the LLVM compiler
infrastructure to perform LLVM byte-code optimizations.  A large list
of these optimizations is available through the llvm2aa command-line.
For more details, see LLVM documentation at http://www.llvm.org.
\end{itemize}
